InnoDB Full text Search hacking with Shiny/R

### 2015-12-26 article.rmd
Fixes.
Fixes

---
title: "Full text search hack with Shiny/R"
author: "Emanuel Calvo"
date: "December 22, 2015"
output: html_document
runtime: shiny
---

```{r init, message = FALSE, echo=FALSE}
options(width = 9999)
knitr::opts_chunk$set(width=9999)

@@

source('~/git/fts_article/load.R')

@@

@@

As we can observ on the previous examples, the query extension algorithm has some noisy produced by the double query
generated in order to join  the results. Also, it won't matter if you have the exact match twice, as the algorithm does not
focus on the exact matches, instead it will relate the occurrences on the first search (where the match happens) and the
sencond (where the algorithm searches for the words that appear in the same phrase than the exact match). That means 
that it is possible to have a high rank without have any matching occurrence.

@@

```
node1 [localhost] {msandbox} (test) > select * from information_schema.INNODB_FT_INDEX_TABLE WHERE DOC_ID = 733 AND lower(WORD) like '%country%';
+------------------+--------------+-------------+-----------+--------+----------+
| WORD             | FIRST_DOC_ID | LAST_DOC_ID | DOC_COUNT | DOC_ID | POSITION |
+------------------+--------------+-------------+-----------+--------+----------+
| country          |          149 |         787 |        28 |    733 |      265 |
| country          |          149 |         787 |        28 |    733 |     1342 |
| countrydistricts |          733 |         733 |         1 |    733 |      816 |
| thecountry       |          249 |         733 |         2 |    733 |      750 |
+------------------+--------------+-------------+-----------+--------+----------+
4 rows in set (0,08 sec)

node1 [localhost] {msandbox} (test) > select * from information_schema.INNODB_FT_INDEX_TABLE WHERE DOC_ID = 155 AND lower(WORD) like '%country%';
+---------+--------------+-------------+-----------+--------+----------+
| WORD    | FIRST_DOC_ID | LAST_DOC_ID | DOC_COUNT | DOC_ID | POSITION |
+---------+--------------+-------------+-----------+--------+----------+
| country |          149 |         787 |        28 |    155 |       31 |
| country |          149 |         787 |        28 |    155 |      495 |
| country |          149 |         787 |        28 |    155 |      158 |
| country |          149 |         787 |        28 |    155 |      525 |
+---------+--------------+-------------+-----------+--------+----------+
4 rows in set (0,09 sec)

@@

>>>>

---
title: "InnoDB Full text Search hacking with Shiny/R"
author: "Emanuel Calvo"
date: "December 22, 2015"
output: html_document
runtime: shiny
---

```{r init, message = FALSE, echo=FALSE}
#options(width = 9999)
#knitr::opts_chunk$set(width=9999)

@@

#Comment if you want to avoid reload all the data
#source('~/fts_article/load.R')

@@

As we can observ on the previous examples, the query extension algorithm has some noisy produced by the double query
generated in order to join  the results. Also, it won't matter if you have the exact match twice, as the algorithm does not
focus on the exact matches, instead it will relate the occurrences on the first search (where the match happens) and the
sencond (where the algorithm searches for the words that appear in the same phrase than the exact match). That means 
that it is possible to have a high rank without have any exact matching occurrence.

The interesting case is the following row, which has 2 exact occurrences and it is not the highest rank using query
extension. Remember, this is expected.

```
| "country districts. As Lucca had five gates, he divided his own country"  | 1,63      |     51 |           8 |   72 |
```

Even worst when using large sentences. In the example bellow you will see the same query, against the table 
storing by paragraph. The boolean rank shows some of the entries way above others, however the query extension
locates at the top records that not necessarily has a lot of exact matches.

@@

@@

```
(test) > select * 
          from information_schema.INNODB_FT_INDEX_TABLE 
          WHERE DOC_ID = 733 AND lower(WORD) like '%country%';
+------------------+--------------+-------------+-----------+--------+----------+
| WORD             | FIRST_DOC_ID | LAST_DOC_ID | DOC_COUNT | DOC_ID | POSITION |
+------------------+--------------+-------------+-----------+--------+----------+
| country          |          149 |         787 |        28 |    733 |      265 |
| country          |          149 |         787 |        28 |    733 |     1342 |
| countrydistricts |          733 |         733 |         1 |    733 |      816 |
| thecountry       |          249 |         733 |         2 |    733 |      750 |
+------------------+--------------+-------------+-----------+--------+----------+
4 rows in set (0,08 sec)

(test) > select * 
          from information_schema.INNODB_FT_INDEX_TABLE 
          WHERE DOC_ID = 155 AND lower(WORD) like '%country%';
+---------+--------------+-------------+-----------+--------+----------+
| WORD    | FIRST_DOC_ID | LAST_DOC_ID | DOC_COUNT | DOC_ID | POSITION |
+---------+--------------+-------------+-----------+--------+----------+
| country |          149 |         787 |        28 |    155 |       31 |
| country |          149 |         787 |        28 |    155 |      495 |
| country |          149 |         787 |        28 |    155 |      158 |
| country |          149 |         787 |        28 |    155 |      525 |
+---------+--------------+-------------+-----------+--------+----------+
4 rows in set (0,09 sec)

@@

Now that you can see the general stats, we'll see how much noise has been added with the query extension algorithm.
To do that,  we'll gather all the occurrences using the query extension option and extract only the ones that match 
with the occurrence.
